Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-22 manuscript/appendix.Rmd
Minor final updates

---
title: 'Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"'
short-title: 'Online appendix for "Who Cares About Crackdowns?"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "April 18, 2021"
title-page: false
published: Working paper.
code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
reference-section-title: References
toc: true
appendix: true
editor_options: 
  chunk_output_type: console
---

<!-- supplement.md is generated from supplement.Rmd. Only edit the .Rmd file, *not* the .md file. -->

>>>>

---
title: 'Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"'
short-title: 'Online appendix for "Who Cares About Crackdowns?"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "April 22, 2021"
title-page: false
# published: Working paper.
code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
reference-section-title: References
toc: true
appendix: true
editor_options: 
  chunk_output_type: console
---

### 2021-04-22 manuscript/manuscript.Rmd
Minor final updates

date: "April 18, 2021"
published: Working paper.

@@

<!-- manuscript.md is generated from manuscript.Rmd. Only edit the .Rmd file, *not* the .md file. -->

@@

INGOs receive funds from a variety of public and private sources. Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions. Private sources include foundations, private corporations, and individuals. While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles in acquiring funding. Closing civic space has resulted in net losses of income to INGOs, particularly in official bilateral and multilateral aid [@DupuyPrakash:2018]

>>>>

date: "April 22, 2021"
published: "Under review at *Global Policy*"

@@

@@

INGOs receive funds from a variety of public and private sources. Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions. Private sources include foundations, private corporations, and individuals. While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles in acquiring funding. Closing civic space has resulted in net losses of income to INGOs, particularly in official bilateral and multilateral aid [@DupuyPrakash:2018].
